Ricci-Ollivier Curvature of the Rooted Phylogenetic Subtree-Prune-Regraft Graph

### 2015-07-24 curvature.tex
Adding 7 taxa to tables.

\begin{table}
\centering
\caption{Ordinary least squares linear multiple regression of rSPR mean access time against degree and distance.}
\subtable[5 taxa]{\csvautotabular{analysis/5-walks-200K/rspr/mean-access-5-regression.csv}}
\subtable[6 taxa]{\csvautotabular{analysis/6-walks-50K/rspr/mean-access-6-regression.csv}}
\label{tab:regressionMAT}
\end{table}

@@

\begin{table}
\centering
\caption{Ordinary least squares linear multiple regression of rSPR $\delta_1$ against degree, distance, and $\kappa$.}
\subtable[5 taxa]{\csvautotabular{analysis/5-walks-200K/rspr/delta1-5-regression.csv}}
\subtable[6 taxa]{\csvautotabular{analysis/6-walks-50K/rspr/delta1-6-regression.csv}}
\label{tab:regressionDelta}
\end{table}

>>>>

\begin{table}
\centering
\caption{Ordinary least squares linear multiple regression of rSPR mean access time against degree and distance.}
\csvautotabular{tables/mean-access.csv}}
\label{tab:regressionMAT}
\end{table}

@@

\begin{table}
\centering
\caption{Ordinary least squares linear multiple regression of rSPR $\delta_1$ against degree, distance, and $\kappa$.}
\csvautotabular{tables/delta1.csv}}
\label{tab:regressionDelta}
\end{table}
